Numerical simulation of the shallow water circular hydraulic jump

### 2020-06-15 numerics_paper/numerical_chj.tex
Add 3-wave solver.

@@

\section{The shallow water circular hydraulic jump}

@@

\subsubsection{HLLE solver}

\subsubsection{HLLM solver}

>>>>

\usepackage{amsmath}

\newcommand{\W}{{\mathcal W}}

@@

\section{The shallow water circular hydraulic jump}
The shallow water equations in two (horizontal) dimensions are
\begin{align}
    h_t + (hu)_x + (hv)_y & = 0 \\
    (hu)_t + \left(hu^2 + \frac{1}{2}gh^2\right)_x + (huv)_y & = 0 \\
    (hv)_t + (huv)_x + \left(hv^2 + \frac{1}{2}gh^2\right)_y & = 0.
\end{align}
These can be written in vector form as
\begin{align}
    q_t + f(q)_x + g(q)_y & = 0.
\end{align}

@@

\subsubsection{HLLE (2-wave) solver}
The HLLE solver approximates the Riemann solution using two waves with
speeds $s_1, s_2$.  The middle state is
\begin{align} \label{qm-HLL}
    q_m^\textup{HLLE} = \frac{f(q_l) - f(q_r) + s_2 q_r - s_1 q_l}{s_2 - s_1}.
\end{align}

\subsubsection{A 3-wave solver}
Refinements of the HLLE solver were subsequently introduced in order to better
resolve contact and shear waves, which are strongly dissipated by the HLLE solver.
In the shallow water equations, we have only a shear wave.  We can introduce a third
wave in the approximate Riemann solver that carries the jump in the transverse velocity.
For simplicity, we describe this solver for an x-interface; i.e. where $u$ is the normal
velocity component and $v$ is the tangential velocity component.  Then the Riemann
solution is assumed to consist of 3 jump-discontinuities $\W^1, \W^*, \W^2$ where $\W^{1,2}$
carry all of the jump in $h$ and $hu$ while $\W^*$ carries all of the jump in $hv$.

The values $h_m$ and $u_m$, along with the speeds for the waves $\W^1,\W^2$ 
are thus determined by the same formula \eqref{qm-HLL} as in the HLL solver.
The speed of the middle wave is determined by conservation:
$$
    s^* = \frac{h_r v_r - h_l v_l}{h_r u_r v_r - h_l u_l v_l}.
$$
The middle state transverse velocity $v_*$ is given by $v_l$ if $s^*>0$ or $v_r$ if $s^*<0$.
